Revision Plan for SIGCOMM'24 Paper \#293

### 2024-05-18 revision_plan.tex
update

\noindent\textcolor{blue}{\textbf{Response 5:} }

>>>>

\noindent\textcolor{blue}{\textbf{Response 5:}
Thanks for the reviewer’s comments. 
Actually, we record the maximum value of the window from the beginning of the flow until now as MW (Maximum Window).
In Section 2.3, we first show how much DCTCP can benefit from padding the spare bandwidth to MW and plot the results in Figure 2.
Moreover, we show that padding the spare bandwidth to MW is just suitable without wasting bandwidth or causing congestion through experiments, and we plot the results of our experiments in Figure 3.
}
